Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-07-31 mu/article/article.tex
Including last BMS changes.

\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
\usepackage{amsmath}    % need for subequations 
\usepackage{graphicx}   % need for figures 
\usepackage{verbatim}   % useful for program listings 
\usepackage{color}      % use if color is used in text 
\usepackage{subfigure}  % use for side-by-side figures 
\usepackage{hyperref}   % use for hypertext links, including those to external 
                        % documents and URLs 
%\usepackage{blindtext}  % fill text 
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
%\usepackage[capitalize]{cleveref}
% \usepackage{showframe}
\usepackage[inline]{showlabels}
\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
 % \input{/Users/bms/util/definitions}

\raggedbottom           % don't add extra vertical space

@@

\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
\author{Reinaldo Zapata-Pe\~na and
        Bernardo S. Mendoza}
\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
Guanajuato 37150, M\'exico}
\author{Anatoli I. Shkrebtii}
\affiliation{University of Ontario, Institute of Technology,
Oshawa, ON, L1H 7L7, Canada}

@@

\begin{abstract}
We present a theoretical study of spin-velocity injection with linearly
polarized light of two 50\% hydrogenated noncentrosymmetric graphene structures:
Alt and Up. We analyzed the cases when the spin is polarized perpendicularly to
the surface of the structures, in the $z$ direction, and wen the spin moves
along the fixed $x$ and $y$ directions. The results are calculated in a full
electronic band structure scheme within DFT in the LDA approximations showing an
anisotropic behavior. We obtained maximum absolute values of
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s for the Up
structure and $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s for the
Alt structure being both structures excellent candidates for spintronics
applications.
\end{abstract}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Side (top panel) and top (bottom panel) views of the Up
      structure along with the 
      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
      labeled 1 (2).
}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Side (top panel) and top (bottom panel) views of the Alt
      structure along with the 
      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
      labeled 1 (2).
}
    \label{fig:alt-struc}
\end{figure}

Using those structures we address a theoretical study of the 
spin velocity
injection (SVI) 
by one-photon absorption of linearly polarized light.
% 
% We calculated the responses for the particular cases when the spin of
% electrons is directed along the the $z$ Cartesian coordinate, perpendicular
% to the $xy$ plane of the structure, or for the case when the velocity is
% directed along the $x$ and $y$ Cartesian direction on the $xy$ plane of the
% structures.
{
% \color{red}
% 
Because we have 2D structures we made the analysis for tow cases. The first is
fixing the spin of the electrons along the $z$ Cartesian direction with the
velocity directed on the surface of the structure in the $xy$ plane. The second
is fixing the spin velocity in the $x$ or $y$ direction and the spin directed
in $xyz$.}
% 
The SVI is an optical effect that quantifies the velocity at which a PSC moves
along the Cartesian direction $\mathrm{a}$ with the spin of electron polarized
along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
polarized light can promote an even distribution of electrons in $\mathbf{k}$ space
regardless the symmetry of the material resulting in a 
null electrical current.\cite{bhatPRL05}
Then, the electrons excited to the conduction bands at opposite $\mathbf{k}$
points will result in opposite spin polarizations producing no net spin
injection.\cite{bhatPRL05} If the crystalline structure of the material is
noncentrosymmetric the spin polarization injected at a given $\mathbf{k}$ point
not necessarily 
 vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88} 
and then, since the velocities of electrons at opposite $\mathbf{k}$ points are
opposite, a PSC will be produced. Since the structures presented
here are noncentrosymmetric, they are good candidates in which this effect can
be induced.

@@

\nonumber\\
&\times 

@@

small, and is neglected throughout this work.\cite{??}

@@

\mathrm{Tr} \left( \frac{\partial \hat{{\rho}}}{\partial t} \hat\calo \right)

@@

r^{\mathrm{a}}_{cv}(\bfk)  r^{\mathrm{b}}_{vc'}(\bfk)  \times
\nonumber \\
& \left( \frac{1}{\omega - \omega_{c'v}(\bfk)  - i\epsilon} - 

@@

\\
\times\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}(\bfk) 

@@

%\subsection{Spin velocity injection} % (fold)
%\label{sec:theory-pure_spin_current}
Now, we define the spin velocity injection (SVI) as
\begin{equation}\label{eq:vab-w}
\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
\end{equation}  
that gives the velocity, along the direction $\mathrm{a}$, at which the spin
moves polarized along the direction $\mathrm{b}$. The carrier injection rate
$\dot n(\go)$ is written as,\cite{nastosPRB05}
\begin{equation}
\dot{n}(\omega) =
\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
\label{eq:dotn}
\end{equation}
where the tensor 
\begin{equation}\label{eq:xi}
\begin{aligned}
\xi^{\mathrm{ab}}(\omega)
&
=
\frac{2\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}k}{8 \pi^{3}}
\\\nonumber
&\times \sum_{vc}
r^{\mathrm{a}}_{vc'}(\bfk)  
r^{\mathrm{b}}_{cv }(\bfk)  
\delta(\omega-\omega_{cv}(\bfk) 
, 
\end{aligned}
\end{equation}
is related to the imaginary part of the linear optical 
response tensor by
$\mathrm{Im}[\ge^{\rma\rmb}(\go)]=2\pi\ge_0\hbar\xi^{\rma\rmb}(\go)$.

@@

Fixing the calculated velocity along $\rma=x$ or $\rma=y$
 we define it's corresponding magnitude as
\begin{align}
\mathcal{V}_{\mathrm{a}}&(\omega,\alpha) \equiv \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
},
\label{eq:vv-mag}
\end{align}
from where we see that the spin would be oriented
in the $xyz$ system's coordinates
according to a polar angle
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{\mathcal{V}_{\mathrm{a}}(\omega,\alpha)} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\end{align}
and an azimuthal angle
\begin{align}
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{plots/2-vab-str-comp}
\caption{$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ 
  vs. $\hbar\go$, for the values of $\ga$ that maximize the signal. The low
  energy regions for the Alt and Up structures start at the energy gap of each
  structure, while in the high energy regions, the values of
  $\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ are also very large. The bottom panel
  corresponds to CdSe and GaAs. }
\label{fig:vab-str-comp}
\end{figure}

@@

Likewise for the Alt structure we find that also $\rma\rmb=yz$ and
$\ga=150^\circ$ maximizes the response, where two extreme values of
$\calv^{\rmy\rmz}$ are found, one at {\color{red} $\hbar\go=0.7204$\,eV} of
$\calv^{\rmy\rmz}=-711.9$ Km/s, and the other at $\hbar\go=0.911$\,eV of
$\calv^{\rmy\rmz}=-330.6$ Km/s.
% 
For the bulk structures we calculate $\calv^{\rma\rmb}(\go)$ from
Eq.~\eqref{eq:vab-w} by simply using $\bfgmu_{\mathrm{max}}$. For CdSe we find
that for $\hbar\go=0.844$\,eV, $\bfgmu_{\mathrm{max}}\to \mu^{zzzz}$, and
$\calv^{\rmz\rmz}(\go)=-59.0$ Km/s, and for GaAs at $\hbar\go=2.324$\,eV,
$\bfgmu_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and $\calv^{\rma\rma}(\go,\ga)=-28.7$\,Km/s, with
$\rma=x,y,z$. For these bulk semiconductors the $x$, $y$, and $z$ axis are
taken along the standard cubic unit cell directions, [100], [010], and [001],
respectively. In Table \ref{tab:vab-str-comp} we present the comparison of
$\calv^{\rma\rmb}(\go,\ga)$ for the 2D structures and bulk crystals.
% 
We remark that, as shown in the figure, 
the 2D structures have maxima in 
$\calv^{\rma\rmb}(\go;\ga)$  
that are bigger
than for the bulk crystals; in particular the Alt
structure gives a $\calv^{\rma\rmb}(\go;\ga)$ $\sim$12 times larger than
that of CdSe and GaAs.
\begin{table}%[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
Up    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
      &      &       & 1.954  & $\mathrm{yz}$ &  266.3 \\
      &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
Alt   & 2D   & 150   & {\color{red}0.720}  & $\mathrm{yz}$ & -711.9 \\
      &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
CdSe  & bulk & --    & 0.844  & $\mathrm{zz}$ &  -59.0 \\
GaAs  & bulk & --    & 2.324  & $\mathrm{xx}$ &  -28.7 \\
\hline
\end{tabular}
\caption{Comparison of the reported maximum values of
$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ for the different structures and their
corresponding polarization angle $\alpha$ and $\hbar\go$ energy values.
}
\label{tab:vab-str-comp}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{upplots/up-vsz-w1}
\caption{For the Up structure, the top panel shows 
$\calv_{\gs^\rmz}(\go,\ga)$ vs. $\hbar\go$ and $\ga$, and the bottom panel
shows $\gamma_{\gs^\rmz}(\go,\ga)$ (right scale, red line), and
$\calv_{\gs^\rmz}(\go,\ga)$ (left scale, black line), vs. $\ga$, for
$\hbar\go=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
\label{fig:up-vsz-w1}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{upplots/up-vsz-w2}
\caption{For the Up structure, the top panel shows $\calv_{\gs^\rmz} (\go,\ga)$
vs. $\hbar\go$ and $\ga$, and the bottom panel shows $\gamma_{\gs^\rmz}
(\go,\ga)$ (right scale, red line), and $\calv_{\gs^\rmz} (\go,\ga)$ (left
scale, black line), vs. $\ga$, for $\hbar\go=1.954$\,eV, i.e. along the
highest ridge shown in the 3D plot. }
\label{fig:up-vsz-w2}
\end{figure}

@@

In the top panel of Fig. \ref{fig:up-vsz-w1} we plot
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
0.080\,eV$\leq\hbar\go\leq$0.096\,eV {\color{red}(same energy range for the Up
structure shown in the left panel of Fig.~\ref{fig:vab-str-comp} )} and
$0^\circ\leq\ga\leq 180^\circ$.
% 
We see a broad peak that maximizes at $\ga=35^{\circ}$ and $\hbar\go=
0.084$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
739.7$\,Km/s, and that the variation of $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ as a function of $\ga$, that comes from the interplay of the
$\bfgmu$ tensor components as multiplied by the  trigonometric functions of
Eq.~\eqref{eq:vab-aw}, gives a sizable set of values between 739.7\,Km/s and
165.4\,Km/s, for 0.084\,eV$\leq\hbar\go\leq$0.090\,eV. 
% 
In the bottom panel, we show $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.084$\,eV,
{\color{red}thus following the ridge shown in the 3D plot of the top panel,
along with its corresponding velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$
(right scale, red line)}.
% 
It is very interesting to see that $\gamma_{\gs^z}(\omega,\alpha)$ is centered
at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$,
for the whole range of $\ga$. This results means that for $\hbar\go=0.084$ eV
and for all values of $\ga$, the electrons, with the chosen spin pointing along
$z$, will move at angle of {\color{red}$\gamma_{\gs^\rmz}(\omega,\alpha) \sim
64.5^{\circ}$} with respect to the $x$ direction, with the range of  high
speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
% 
Also, from Eq. \eqref{eq:gamma-par} we find that
$\gamma^\parallel_{\gs^\mathrm{z}} (\omega,\alpha)=\ga = 64.56^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see green
arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.50^\circ$,
gives $\ga=154.50^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
arrow); thus, at $\hbar\go=0.084$ eV, an incident field polarized at $\alpha
\sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
polarized along $z$, that move parallel or perpendicular to the incident
electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.

>>>>

%\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
\documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
\usepackage{amsmath}    % need for subequations 
\usepackage{graphicx}   % need for figures 
\usepackage{verbatim}   % useful for program listings 
\usepackage{color}      % use if color is used in text 
\usepackage{subfigure}  % use for side-by-side figures 
\usepackage{hyperref}   % use for hypertext links, including those to external 
                        % documents and URLs 
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
%\usepackage[inline]{showlabels}
\input{/Users/bms/util/definitions}
\def\tama{10cm}
\raggedbottom           % don't add extra vertical space

@@

\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
\author{Reinaldo Zapata-Pe\~na}
\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
Guanajuato 37150, M\'exico}
\author{Bernardo S. Mendoza}
\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
Guanajuato 37150, M\'exico}
\author{Anatoli I. Shkrebtii}
\affiliation{University of Ontario, Institute of Technology,
Oshawa, ON, L1H 7L7, Canada}

@@

\begin{abstract}
We present a theoretical study of spin-velocity injection of a pure
spin current induced by  a linearly
polarized beam of light that impinges normally at the surface of  two 50\%
hydrogenated noncentrosymmetric 2D graphene 
structures, labeled Up and Alt.
The hydrogenation opens an energy gap in both structures.
We analyze two possibilities, one in which by fixing the spin along a
chosen direction, the resulting spin-velocity is calculated, 
and the other one, where we chose the spin-velocity direction
on the surface plane, and calculate its speed and
spin orientation. We do so by changing the energy $\hbar\go$ 
and polarization angle $\ga$  of the incoming  beam. 
The results are calculated in a full
electronic band structure scheme within the DFT in the LDA approximation.
The maxima of the spin-velocity speed is obtained when
$\hbar\go=0.084$\,eV and $\ga=35^\circ$ for Up,
and
$\hbar\go=0.720$\,eV and $\ga=150^\circ$ for Alt.
We find a speed of
668\,Km/s
and 
645\,Km/s
for Up and Alt, respectively, when the spin points perpendicular to
the surface. Also,
the response is maximized
by fixing the spin-velocity direction along a high symmetry Cartesian axis,
obtaining a speed of 
688\,Km/s 
and the spin  pointing at 13$^\circ$ form the surface normal, for Up,
and
906\,Km/s 
and the spin pointing at 60$^\circ$ from the surface normal, for Alt.
These speed values are larger than those of bulk semiconductors, like
CdSe and GaAs, thus 
making the hydrogenated graphene structures
 excellent candidates for spintronics
applications.
\end{abstract}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\tama]{figures/upstruc2}
    \\
    \includegraphics[width=\tama]{figures/upstruc1}
    \caption{Side (top panel) and top (bottom panel) views of the Up
      structure along with the 
      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
      labeled 1 (2).
}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\tama]{figures/altstruc2}
    \\
    \includegraphics[width=\tama]{figures/altstruc1}
    \caption{Side (top panel) and top (bottom panel) views of the Alt
      structure along with the 
      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
      labeled 1 (2).
}
    \label{fig:alt-struc}
\end{figure}

Using those structures we address a theoretical study of the 
spin velocity
injection (SVI) 
by one-photon absorption of linearly polarized light.
Because we have 2D structures we made the analysis for tow cases. The first is
fixing the spin of the electrons along the $z$ Cartesian direction with the
velocity directed on the surface of the structure in the $xy$ plane. The second
is fixing the spin velocity in the $x$ or $y$ direction and the spin directed
in $xyz$.
% 
The SVI is an optical effect that quantifies the velocity at which a PSC moves
along the Cartesian direction $\mathrm{a}$ with the spin of electron polarized
along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
polarized light can promote an even distribution of electrons in $\mathbf{k}$ space
regardless the symmetry of the material resulting in a 
null electrical current.\cite{bhatPRL05}
Then, the electrons excited to the conduction bands at opposite $\mathbf{k}$
points will result in opposite spin polarizations producing no net spin
injection.\cite{bhatPRL05} If the crystalline structure of the material is
noncentrosymmetric the spin polarization injected at a given $\mathbf{k}$ point
not necessarily 
 vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88} 
and then, since the velocities of electrons at opposite $\mathbf{k}$ points are
opposite, a PSC will be produced. Since the structures presented
here are noncentrosymmetric, they are good candidates in which this effect can
be induced.

@@

@@

small, and is neglected throughout this work.\cite{nastosPRB07}

@@

\mathrm{Tr} \left( \dot{\hat\rho} \hat\calo \right)

@@

r^{\mathrm{a}}_{cv}(\bfk)  r^{\mathrm{b}}_{vc'}(\bfk)  
\left( \frac{1}{\omega - \omega_{c'v}(\bfk)  - i\epsilon} - 

@@

\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}(\bfk) 

@@

%\subsection{Spin velocity injection} % (fold)
%\label{sec:theory-pure_spin_current}
Now, we define the spin velocity injection (SVI) as
\begin{equation}\label{eq:vab-w}
\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
\end{equation}  
that gives the velocity, along the direction $\mathrm{a}$, at which the spin
moves polarized along the direction $\mathrm{b}$. The carrier injection rate
$\dot n(\go)$ is written as,\cite{nastosPRB05}
\begin{equation}
\dot{n}(\omega) =
\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
\label{eq:dotn}
\end{equation}
where the tensor 
\begin{equation}\label{eq:xi}
\begin{aligned}
\xi^{\mathrm{ab}}(\omega)
&
=
\frac{2\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}k}{8 \pi^{3}}
 \sum_{vc}
r^{\mathrm{a}}_{vc'}(\bfk)  
r^{\mathrm{b}}_{cv }(\bfk)  
\delta(\omega-\omega_{cv}(\bfk) 
, 
\end{aligned}
\end{equation}
is related to the imaginary part of the linear optical 
response tensor by
$\mathrm{Im}[\ge^{\rma\rmb}(\go)]=2\pi\ge_0\hbar\xi^{\rma\rmb}(\go)$.

@@

Fixing the calculated velocity along $\rma=x$ or $\rma=y$
 we define it's corresponding magnitude as
\begin{align}
\mathcal{V}_{\mathrm{a}}(\omega,\alpha) \equiv 
\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
},
\label{eq:vv-mag}
\end{align}
from where we see that the spin would be oriented
in the $xyz$ system's coordinates
according to a polar angle
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
= 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{\mathcal{V}_{\mathrm{a}}(\omega,\alpha)} \right),
 \quad 0 \leq \theta \leq \pi, 
\label{eq:polar-ang}
\end{align}
and an azimuthal angle
\begin{align}
\varphi_{\mathrm{a}} (\omega,\alpha)
=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\quad 0 \leq \varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=\tama]{plots/2-vab-str-comp}
\caption{$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ 
  vs. $\hbar\go$, for the values of $\ga$ that maximize the signal. The low
  energy regions for the Alt and Up structures start at the energy gap of each
  structure, while in the high energy regions, the values of
  $\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ are also very large. The bottom panel
  corresponds to CdSe and GaAs. }
\label{fig:vab-str-comp}
\end{figure}

@@

Likewise for the Alt structure we find that also $\rma\rmb=yz$ and
$\ga=150^\circ$ maximizes the response, where two extreme values of
$\calv^{\rmy\rmz}$ are found, one at  $\hbar\go=0.720$\,eV of
$\calv^{\rmy\rmz}=-711.9$ Km/s, and the other at $\hbar\go=0.911$\,eV of
$\calv^{\rmy\rmz}=-330.6$ Km/s.
% 
For the bulk structures we calculate $\calv^{\rma\rmb}(\go)$ from
Eq.~\eqref{eq:vab-w} by simply using $\bfgmu_{\mathrm{max}}$. For CdSe we find
that for $\hbar\go=0.844$\,eV, $\bfgmu_{\mathrm{max}}\to \mu^{zzzz}$, and
$\calv^{\rmz\rmz}(\go)=-59.0$ Km/s, and for GaAs at $\hbar\go=2.324$\,eV,
$\bfgmu_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and $\calv^{\rma\rma}(\go,\ga)=-28.7$\,Km/s, with
$\rma=x,y,z$. For these bulk semiconductors the $x$, $y$, and $z$ axis are
taken along the standard cubic unit cell directions, [100], [010], and [001],
respectively. In Table \ref{tab:vab-str-comp} we present the comparison of
$\calv^{\rma\rmb}(\go,\ga)$ for the 2D structures and bulk crystals.
% 
We remark that, as shown in the figure, 
the 2D structures have maxima in 
$\calv^{\rma\rmb}(\go;\ga)$  
that are bigger
than for the bulk crystals; in particular the Alt
structure gives a $\calv^{\rma\rmb}(\go;\ga)$ $\sim$12 times larger than
that of CdSe and GaAs.
\begin{table}%[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
Up    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
      &      &       & 1.954  & $\mathrm{yz}$ &  266.3 \\
      &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
Alt   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
      &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
CdSe  & bulk & --    & 0.844  & $\mathrm{zz}$ &  -59.0 \\
GaAs  & bulk & --    & 2.324  & $\mathrm{xx}$ &  -28.7 \\
\hline
\end{tabular}
\caption{Comparison of the reported maximum values of
$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ for the different structures and their
corresponding polarization angle $\alpha$ and $\hbar\go$ energy values.
}
\label{tab:vab-str-comp}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{upplots/up-vsz-w1}
\caption{For the Up structure, the top panel shows 
$\calv_{\gs^\rmz}(\go,\ga)$ vs. $\hbar\go$ and $\ga$, and the bottom panel
shows $\gamma_{\gs^\rmz}(\go,\ga)$ (right scale, red line), and
$\calv_{\gs^\rmz}(\go,\ga)$ (left scale, black line), vs. $\ga$, for
$\hbar\go=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
\label{fig:up-vsz-w1}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{upplots/up-vsz-w2}
\caption{For the Up structure, the top panel shows $\calv_{\gs^\rmz} (\go,\ga)$
vs. $\hbar\go$ and $\ga$, and the bottom panel shows $\gamma_{\gs^\rmz}
(\go,\ga)$ (right scale, red line), and $\calv_{\gs^\rmz} (\go,\ga)$ (left
scale, black line), vs. $\ga$, for $\hbar\go=1.954$\,eV, i.e. along the
highest ridge shown in the 3D plot. }
\label{fig:up-vsz-w2}
\end{figure}

@@

In the top panel of Fig. \ref{fig:up-vsz-w1} we plot
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
0.080\,eV$\leq\hbar\go\leq$0.096\,eV (similar energy range for the Up
structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
$0^\circ\leq\ga\leq 180^\circ$.
% 
We see a broad peak that maximizes at $\ga=35^{\circ}$ and $\hbar\go=
0.084$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
739.7$\,Km/s, and that the variation of $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ as a function of $\ga$, that comes from the interplay of the
$\bfgmu$ tensor components as multiplied by the  trigonometric functions of
Eq.~\eqref{eq:vab-aw}, gives a sizable set of values between 739.7\,Km/s and
165.4\,Km/s, for 0.084\,eV$\leq\hbar\go\leq$0.090\,eV. 
% 
In the bottom panel, we show $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.084$\,eV,
thus following the ridge shown in the 3D plot of the top panel. 
Also,
we plot the
corresponding velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$
(right scale, red line),
where it is very interesting to see that $\gamma_{\gs^z}(\omega,\alpha)$ is centered
at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$,
for the whole range of $\ga$. This results means that for $\hbar\go=0.084$ eV
and for all values of $\ga$, the electrons, with the chosen spin pointing along
$z$, will move at angle of $\gamma_{\gs^\rmz}(\omega,\alpha) \sim
64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
% 
Also, from Eq. \eqref{eq:gamma-par} we find that
$\gamma^\parallel_{\gs^\mathrm{z}} (\omega,\alpha)=\ga = 64.56^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see green
arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.50^\circ$,
gives $\ga=154.50^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
arrow); thus, at $\hbar\go=0.084$ eV, an incident field polarized at $\alpha
\sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
polarized along $z$, that move parallel or perpendicular to the incident
electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.

Now, we analyze the results for the second energy range of the Up structure
shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel
of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\go\leq$1.960\,eV and
$0^\circ\leq\ga\leq 180^\circ$.
% 
We see two broad peaks that maximize at $\ga=35^{\circ}$ and $\hbar\go=
1.954$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
193.5$\,Km/s, and $\ga=35^{\circ}$ and $\hbar\go= 1.957$\,eV, with a value
of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) = 170.6$\,Km/s. 
% 
We only analyze the highest  maximum in the bottom panel, where we  show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\ga$ (left scale,
black line), at $\hbar\go= 1.954$\,eV, thus following the highest ridge shown
in the 3D plot of the top panel. Also we plot the corresponding
velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$ (right scale, red
line),
where in
this case we see that the values of $\gamma_{\gs^z}(\omega,\alpha)$ have more
dispersion, as a function of $\ga$, than for the lower energy range shown in
the bottom panel of Fig.~\ref{fig:up-vsz-w1}.
% 
However, $\gamma_{\gs^z}(\omega,\alpha)\sim 77.8^\circ$ is constant from
$\ga=0^\circ$ and up to $\ga\sim 85^\circ$. In this case, we find that
$\gamma^\parallel_{\gs^\mathrm{z}}(\omega,\alpha)=\ga=78.0^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (see green
arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=167.8^\circ$, gives
$\ga=77.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
65.6$\,Km/s (see blue arrow). 
% 
Thus, by the correct choice of $\hbar\go$ and $\alpha$ we could inject
electrons, in this case with their spin polarized along $z$, that move parallel
or perpendicular to the incident electric field, with finite speeds.
